%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Consultant, Data Scientist} % Job title
    {Guidehouse, formerly PricewaterhouseCoopers Public Practice} % Organization
    {Washington, DC} % Location
    {Jan. 2019 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Leads three client engagement teams consisting of consultants, data analysts, data scientists, and data engineers that design and develop business intelligence (BI) and predictive models for intelligence community clients.}
        \item {Leverages Python, SQL, Tableau and other Data Science tools to answer key intelligence questions and inform executive level business decisions impacting agency and community-wide operations.}
        \item {Evaluates enterprise DW architecture feasibility, risk and technologies related to business change (i.e. assessing, identifying and recommending BI and related business stakeholders' data requirements; BI solution prototyping and development; processes and performance from business and technical standpoints; and the impact of data changes on business and/or IT processes).}
        \item {Develops and validates business stakeholders' conceptual data models, including socializing and implementing logical and physical DW/data mart models; identifying data sources and metadata (including business rules, definitions, attributes) to deliver analytic requirements.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Data Analyst} % Job title
    {Intelligence Systems Support Office} % Organization
    {Tampa, FL} % Location
    {Aug. 2018 - Jan. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led diverse projects in a dynamic and collaborative environment developing understanding of established enterprise tools/processes while pursuing advanced approaches using data science techniques and methods.}
        \item {Leveraged advanced data science techniques (Kibana, R, Python, Tableau) to perform qualitative, quantitative, and mixed methods research and analysis for SES and GOFO consumption.}
        \item {Pursued innovation opportunities while delivering real results to move projects forward and answer key intelligence questions in an enterprise R\&D environment.}
        \item {Developed research plans, conducted research, performed problem solving and applied novel solutions from the best of academia, open source, and the commercial sector against challenging problems from across the Department of Defense and the Intelligence Community.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Associate, Data Analytics} % Job title
    {New York Life} % Organization
    {Tampa, FL} % Location
    {Sep. 2017 - Aug. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created advanced management dashboards and data visualizations, recurring and ad hoc reports, and analysis to ensure accuracy and high level of value added for senior leader consumption.}
        \item {Utilized R, Toad, and SQL Server to automate recurring reports and participated in process improvement and cost reduction projects across the company.}
        \item {Developed workforce projections that were tied to company operating plan and created/executed reports supporting quality control activities.}
        \item {Led studies and evaluations that assessed the effectiveness of operations, provided input to future investments, measured return on investments, and evaluated performance against goals and objectives.}
        \item {Developed and maintained accurate and timely operations reports that provided senior leaders with the information needed to evaluate and improve business performance, develop key workforce projections, and support company strategy.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Analytic Methodologist} % Job title
    {U.S. Central Command} % Organization
    {Tampa, FL} % Location
    {Oct. 2016 - Sep. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Evaluated influence operations information from a variety of sources leveraging innovative methods to identify, analyze and solve problems for CENTCOM leadership and J39 decision makers.}
        \item {Using data science techniques, collected, analyzed and disseminated raw data and finished intelligence products identifying trends, pattern profiles, and estimates for CENTCOM.}
        \item {Led analytics projects and statistical analysis of qualitative and quantitative data in coordination with statisticians, scientists, researchers and planners to achieve mission success in supporting CENTCOM operations.}
        \item {Conducted studies and evaluations aimed at determining of the effectiveness of CENTCOM operations, providing input to future investments, measuring return on investments, and evaluating performance.}
        \item {Conducted quality control of analytic proposals regarding standard, non-standard or emerging research methods and analysis to assess business performance and operations success.}
        \item {Served as a liaison to international partners and USGOV personnel for theater-wide analysis activities related to Operation Inherent Resolve (OIR).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Business Analytics Officer} % Job title
    {National Geospatial-Intelligence Agency} % Organization
    {Springfield, VA} % Location
    {Aug. 2015 - Oct. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Utilized statistics, mathematical modeling, systems analysis, logic, comparative analysis, data basing, and quantitative graphics to provide technical input into the development, evaluation, utilization, and deployment of solutions and improvements to optimize GEOINT analysis and production.}
        \item {Conducted studies and evaluations aimed at determining of the effectiveness of NGA's programs, provided input to future NGA investments, and evaluated other agency-wide major issues.}
        \item {Applied operations research techniques to shape studies, analyze data, and portray results and visual representations that were easily understood by the consumer.}
        \item {Generated Terms of Reference, developed study and analysis methodologies, applied methodologies, and prepared final reports for NGA senior leadership.}
        \item {Educated management and analysts in quantitative methodologies as they applied to applicable analysis.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Program Analyst} % Job title
    {U.S. Department of Homeland Security} % Organization
    {Washington, DC} % Location
    {Sep. 2013 - Aug. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Leveraged internal databases to analyze and communicate organizational performance for the Executive Secretary, Chief of Staff, Deputy Secretary and Secretary.}
        \item {Established a metrics and analytics program for the Office of the Executive Secretariat, utilizing statistical methodologies to depict key performance indicators in a concise and coherent manner.}
        \item {Documented key business processes using process design methodology and mapping techniques resulting in optimized processes and cost savings. Identified disconnects and gaps, suggested performance metrics, provided analysis that served as the foundation for process improvements and knowledge transfer across the agency on how the Division's processes worked.}
        \item {Developed an executive dashboard for senior leadership depicting performance trends across the Department as it pertained to Congressional correspondence, both classified and unclassified.}
        \item {Conducted qualitative and quantitative analysis of the Department’s nationwide logistics programs and program sub-components, including law enforcement fleet management, personal property management, facilities and space management, and budget administration.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Business Analyst} % Job title
    {PACE Center} % Organization
    {Jacksonville, FL} % Location
    {Mar. 2012 - Jun. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Utilized SAP BusinessObjects Web Intelligence XI to develop reports, reporting dashboards, and to analyze organizational performance for C-Level staff.}
        \item {Championed data analytics throughout the organization and its distributed service network by employing industry best practices and analytical methodologies.}
        \item {Designed, modified and administered specific data collection instruments to evaluate programs, processes, and initiatives to support senior leader decision making.}
        \item {Developed weekly, monthly and annual reports to inform executive leadership and Department of Justice stakeholders of the organization's performance as it related to specific goals, milestones and contract measures.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Management and Program Analyst} % Job title
    {U.S. Department of Education} % Organization
    {Washington, DC} % Location
    {Aug. 2010 - Mar. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed, developed, and coordinated Business Performance Review document for use in tracking program and project performance across organization with respect to external reporting and stakeholder requirements.}
        \item {Assisted with development and formation of the Department’s Performance Improvement Office and Officer as required by the GPRA Modernization Act of 2010, while simultaneously contributing to the development and analysis of agency wide priority goals and quarterly performance review framework to improve performance and reduce costs.}
        \item {Served as primary resource for ad hoc and ongoing analysis of programs, projects, and initiatives. All analysis was thoroughly researched, documented, and articulated/presented to provide contextual understanding of new data for the senior managers, including SES leadership.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
